MLH1 Results Outline

### 2020-04-04 doc/Results.rmd
starting a figure for IFDs

@@

>>>>

P1.by.P2_plot <- ggplot(Curated_BivData.22, aes(y = rev(PER_Foci_2), x= PER_Foci_1, color=strain))+
  geom_jitter(alpha=.2)+
  ggtitle("Normalized IFD")+
  scale_color_manual(values=colors_of_strains)+  facet_wrap(sex~subsp, scales = "free")+theme(legend.position="none")+xlim(c(0,1))+ylim(c(0,1))

#each point is a 2CO, with the F1 and F2 position

P1.by.P2_plot_raw <- ggplot(Curated_BivData.22, aes(y = Foci2, x= Foci1, color=strain))+
  geom_jitter(alpha=.2)+
  ggtitle("Normalized IFD")+
  scale_color_manual(values=colors_of_strains)+  facet_wrap(sex~subsp, scales = "free")+theme(legend.position="none")

@@

```{r Q1.IFD.plot, echo=FALSE}

#make interference plots of IFD, position p1 by p2
